---
title: "Int_Iso"
output: html_document
date: "2024-03-28"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Outline

-   load data

-   add volume and mass

Load Libraries

```{r}


libs_1<-c("tidyverse","knitr","psych","reshape2","rmarkdown")

#data manipulation/exploration
libs_2<-c("readxl","readr","tidyr","GGally","naniar","readr")


# plotting
libs_3<-c("ggplot2","viridis","ggpubr","cowplot")#,"ggthemr") 

#ggpubr = package for publishing
#cowplot=  #to create compounded figures

#tables
libs_4<-c("dplyr","stargazer","xlsx","ggplot2","scales","extrafont","writexl")


libs<-c(libs_1,libs_2,libs_3,libs_4)

lapply(libs,require, character.only=TRUE)

```

### Molecular weight calculations

```{r}

MW_NH3=14.007+(3*1.008)
MW_NH4=14.007+(4*1.008)
MW_N = 14.007
MW_H = 1.008
MW_P = 30.974
MW_S = 32.006
MW_Na= 22.9
MW_Mg= 24.305
MW_K=39.098
MW_Cl=35.45
MW_C=12.011
MW_S=32.06
MW_O=15.999
MW_SO4_T=MW_S+(4*MW_O)
MW_H2PO4_T=MW_P+(4*MW_O)+(2*MW_H) ## because the formula uses H2PO4 and in the acidified sample we expect this form
MW_Ac=(2*MW_C)+(3*MW_H)+(2*MW_O)
MW_H2CO3=(MW_C+(3*MW_O)+(2*MW_H))
```

### Converting to mole

```{r}

moles<-data.frame(MW_Na, MW_NH4,MW_K,MW_Mg)
moles_An<-data.frame(MW_Ac, MW_Cl,MW_H2PO4_T, MW_SO4_T,MW_H2CO3)
```

### Setting up mass of biochar and volume of urine dataframe

```{r}

volume<-rep(c(0.0011),times=51)
volume<-data.frame(volume)

mass_biochar<-rep(c(0.4),times=51)
mass_biochar<-data.frame(mass_biochar)
mass_biochar
                  
```

## Extracting Data from Excel Files

```{r}
#isothermFittinglibrary(PUPAIM)

# setwd("/Users/soliverfusi/OneDrive/Desktop/Fusi/Sorption/Final_Data")

path<-"Intermediate_Isotherm.xls"

FullSheet <- path%>%
  excel_sheets()%>% #extracts the sheet name of the file fed to the 'path' function
  set_names() %>%
  map(read_excel,path=path,na=c(common_na_strings,"n.a."))
```

### Cations

```{r}


Cations_all<- data.frame(FullSheet$"Cations"[c(1:51),])

#changing all the columns to numeric (noteably the Ox columns since I use "In" and "A"-"C",
#it registers as a character column

#Cations_all[] <- lapply(Cations_all[], function(x) as.numeric(as.character(x)))
```

### Anions

```{r}

Anions_all<- data.frame(FullSheet$"Anions"[c(1:51),])

#Anions_all[] <- lapply(Anions_all, function(x) as.numeric(as.character(x)))
```

### Influents

```{r}

#Cations
Cations_in<- data.frame(FullSheet$"Cations"[c(52:54),])
#Cations_in[] <- lapply(Cations_in, function(x) as.numeric(as.character(x)))

#Anions
Anions_in<- data.frame(FullSheet$"Anions"[c(52:54),])
#Anions_in[] <- lapply(Anions_in, function(x) as.numeric(as.character(x)))
```

### Controls

```{r}

#Cations
Cations_ctrl<- data.frame(FullSheet$"Cations"[c(55:57),])
#Cations_ctrl[] <- lapply(Cations_ctrl, function(x) as.numeric(as.character(x)))

#Anions
Anions_ctrl<- data.frame(FullSheet$"Anions"[c(55:57),])
#Anions_ctrl[] <- lapply(Anions_ctrl, function(x) as.numeric(as.character(x)))
```

### pH

```{r}

pH <- data.frame(FullSheet$"pH"[c(1:51),])

#pH[] <- lapply(pH, function(x) as.numeric(as.character(x)))
```

renaming columns

```{r}

#naming columns so they can be referenced easily later

## CATIONS
colnames(Cations_all)<-as.character(c('Ox','ID','Rep','Sodium','Ammonium','Potassium','Magnesium'))
#----------------------------------------------------------------------
##ANIONS
colnames(Anions_all)<-as.character(c('Ox','ID','Rep','Acetate','Chloride','Phosphate', 'Sulfate','Carbonate'))

#----------------------------------------------------------------------
## IN
colnames(Cations_in)<-as.character(c('Ox','ID','Rep','Sodium','Ammonium','Potassium','Magnesium'))

colnames(Anions_in)<-as.character(c('Ox','ID','Rep','Acetate','Chloride','Phosphate', 'Sulfate','Carbonate'))
#----------------------------------------------------------------------
##pH 
colnames(pH)<-as.character(c('Ox','ID','Rep','pH'))
#-------------------------------------------------------------------------------
```

### Converting to Moles

```{r}

#converting to moles 

#influent Cations

Cations_in_mol <- mapply('/', Cations_in[,4:7],moles)
Cations_in_mol<-data.frame(cbind(Cations_in[,1:3],Cations_in_mol))
colnames(Cations_in_mol)<-as.character(c('Ox','ID','Rep','Sodium','Ammonium','Potassium','Magnesium'))

#----------------------------------------------------------------------
# Main 8 Cations 

Cations_all_mol<-mapply('/', Cations_all[,4:7],moles)

Cations_all_mol<-data.frame(cbind(Cations_all[,1:3],Cations_all_mol))
colnames(Cations_all_mol)<-as.character(c('Ox','ID','Rep','Sodium','Ammonium','Potassium','Magnesium'))

#----------------------------------------------------------------------

#influent Anions

Anions_in_mol<-mapply('/', Anions_in[,4:8],moles_An)
Anions_in_mol<-data.frame(cbind(Anions_in[,1:3],Anions_in_mol))
colnames(Anions_in_mol)<-as.character(c('Ox','ID','Rep','Acetate','Chloride','Phosphate', 'Sulfate','Carbonate'))
#----------------------------------------------------------------------

# Main 8 Anions

Anions_all_mol<-mapply('/', Anions_all[,4:8],moles_An)

Anions_all_mol<-data.frame(cbind(Anions_all[,1:3],Anions_all_mol))
colnames(Anions_all_mol)<-as.character(c('Ox','ID','Rep','Acetate','Chloride','Phosphate', 'Sulfate', 'Carbonate'))

#----------------------------------------------------------------------

#Ctrls Cations

Cations_ctrl_mol<-mapply('/', Cations_ctrl[,4:7],moles)
Cations_ctrl_mol<-data.frame(cbind(Cations_ctrl[,1:3],Cations_ctrl_mol))
colnames(Cations_ctrl_mol)<-as.character(c('Ox','ID','Rep','Sodium','Ammonium','Potassium','Magnesium'))

#Ctrl Anions 

Anions_ctrl_mol<-mapply('/', Anions_ctrl[,4:8],moles_An)
Anions_ctrl_mol<-data.frame(cbind(Anions_ctrl[,1:3],Anions_ctrl_mol))
colnames(Anions_ctrl_mol)<-as.character(c('Ox','ID','Rep','Acetate','Chloride','Phosphate', 'Sulfate', 'Carbonate'))
```

## Influent (3) Statistics in moles

```{r}

#-------------------------------------------------------------------------------
# CATIONS
# influent samples to long format for easier manipulation
Cations_in_mol_long<-
  Cations_in_mol%>%
  pivot_longer(
    cols=c(Sodium,Ammonium,Potassium,Magnesium),
    names_to ="Cation_Species",
    values_to="Concentration",
    names_repair="minimal")

#calculating the mean and stdev to make sure that variability is acceptable (<5%)
Cations_in_mol_stats <- Cations_in_mol_long %>%
  group_by(Cation_Species) %>%
  summarise(in_mean=mean(Concentration,na.rm=FALSE),
            #.groups='rowwise',
            in_std=sd(Concentration, na.rm=FALSE),
            in_perc_std=in_std/ in_mean*100)
Cations_in_mol_stats<-data.frame(Cations_in_mol_stats)

#-------------------------------------------------------------------------------
# ANIONS
# influent samples to long format for easier manipulation
Anions_in_mol_long<-
  Anions_in_mol%>%
  pivot_longer(
    cols=c(Acetate,Chloride,Phosphate,Sulfate,Carbonate),
    names_to ="Anion_Species",
    values_to="Concentration",
    names_repair="minimal")

#calculating the mean and stdev to make sure that variability is acceptable (<5%)
Anions_in_mol_stats <- Anions_in_mol_long %>%
  group_by(Anion_Species) %>%
  summarise(in_mean=mean(Concentration,na.rm=FALSE),
            #.groups='rowwise',
            in_std=sd(Concentration, na.rm=FALSE),
            in_perc_std=in_std/ in_mean*100)
Anions_in_mol_stats<-data.frame(Anions_in_mol_stats)
#-------------------------------------------------------------------------------
```

## Control Statistics

```{r}

# CATIONS 

#pivoting
Cations_ctrl_mol_long<-
  Cations_ctrl_mol%>%
  pivot_longer(
    cols=c(Sodium,Ammonium,Potassium,Magnesium),
    names_to ="Cation_Species",
    values_to="Concentration",
    names_repair="minimal")

#calculating the mean and stdev to make sure that variability is acceptable (<5%)
Cations_ctrl_mol_stats <- Cations_ctrl_mol_long %>%
  group_by(Cation_Species) %>%
  summarise(ctrl_mean=mean(Concentration,na.rm=TRUE),
            #.groups='rowwise',
            ctrl_std=sd(Concentration, na.rm=TRUE),
            perc_std=ctrl_std/ ctrl_mean*100)
Cations_ctrl_mol_stats<-data.frame(Cations_ctrl_mol_stats)

# ANIONS
Anions_ctrl_mol_long<-
  Anions_ctrl_mol%>%
  pivot_longer(
    cols=c(Acetate,Chloride,Phosphate,Sulfate,Carbonate),
    names_to ="Anion_Species",
    values_to="Concentration",
    names_repair="minimal")

#calculating the mean and stdev to make sure that variability is acceptable (<5%)
Anions_ctrl_mol_stats <- Anions_ctrl_mol_long %>%
  group_by(Anion_Species) %>%
  summarise(ctrl_mean=mean(Concentration,na.rm=FALSE),
            #.groups='rowwise',
            ctrl_std=sd(Concentration, na.rm=FALSE),
            ctrl_perc_std=ctrl_std/ ctrl_mean*100)
Anions_ctrl_mol_stats<-data.frame(Anions_ctrl_mol_stats)

```

## Combining All concentration triplicates into One Large Data Frame

##Combining Anions and Cations into One Dataframe for PHREEQC

-   all the molar concentration of the ions, in triplicate, combined into one dataframe

-   saving the dataframe as an excel file that can be imported into PHREEQC to calculate equilibrium activity.

```{r}

#Combining cations and anions into one dataframe for convenient activity calculations

#----------------------------------------------------------------------
Phreeqc_num<-data.frame(seq(1,nrow(Cations_all_mol)))
colnames(Phreeqc_num)<-("Number")

int_iso_all <- data.frame(rbind(Cations_all_mol[,]),
                           Anions_all_mol[,-c(1:3)],
                           pH[,4])
int_iso_all<-data.frame(cbind(Phreeqc_num[,],int_iso_all))
colnames(int_iso_all)<-as.character(c("PHREEQC_number",'Ox','ID','Rep','Sodium','Ammonium','Potassium','Magnesium','Acetate','Chloride','Phosphate', 'Sulfate', 'Carbonate', "pH"))


int_iso_all_for_PHREEQC<-data.frame(int_iso_all[,c(1,5:14)])

colnames(int_iso_all_for_PHREEQC) = c("Number",'Na','N(-3)','K','Mg','Acetate','Cl','P', 'S(6)', 'C(4)', "pH")

write.table(int_iso_all_for_PHREEQC,"/Users/soliverchefusi/Library/CloudStorage/OneDrive-Personal/Desktop/Fusi/Sorption/AK_to_AO_Isotherm/Final_Data/Activities/int_iso_all_for_PHREEQC.txt", sep = "\t",
            row.names = FALSE, col.names = FALSE)
#----------------------------------------------------------------------
```

##PHREEQC

## Activities

```{r}

int_iso_Act_Ion_str<- data.frame((FullSheet$"Act"[c(1:51),c(4:7)]))

int_iso_Act_Ion_str[,c(2:4)]<-1000*(10^(int_iso_Act_Ion_str[,c(2:4)]))
colnames(int_iso_Act_Ion_str)<-as.character(c("Ionic_str","Act_NH4","Act_Na","Act_K"))


df_All<- data.frame(cbind(int_iso_Act_Ion_str, int_iso_all))
```

## Nov 2023 Edits

-   In is just in, not avg of in and ctrl - started to fix this but ended up still using the avg value

-   #overide definition of In

```{r}

#Cations

Cat_In <- Cations_in_mol_stats[,c(1:3)] %>%
  pivot_wider(names_from = Cation_Species, values_from = c(in_mean, in_std))

Cat_In<-data.frame(data.frame(lapply(Cat_In,rep,times=51)))

colnames(Cat_In)<-c("NH4_In","Mg_In","K_In","Na_In","NH4_std","Mg_std","K_std","Na_std")

#Anions

An_In <- Anions_in_mol_stats[,c(1:3)] %>%
  pivot_wider(names_from = Anion_Species, values_from = c(in_mean, in_std))

An_In<-data.frame(data.frame(lapply(An_In,rep,times=51)))

colnames(An_In)<-c("Ace_In","Carb_In","Cl_In","P_In","S_In","Ace_std","Carb_std","Cl_std","P_std","S_std")
```

Nov 2023 Edits cont.

```{r}
#Standards

#Cations

Cations_ctrl_mol_Avg <- Cations_ctrl_mol %>%
  group_by(group = gl(n() / 3, 3)) %>%  # Create groups of every 3 rows
  summarise_at(vars(Sodium, Ammonium, Potassium, Magnesium), list(mean = ~mean(., na.rm = TRUE), sd = ~sd(., na.rm = TRUE))) %>% 
  select(-1)
colnames(Cations_ctrl_mol_Avg)<-c("Na_ctrl","NH4_ctrl","K_ctrl","Mg_ctrl","Na_ctrl_std","NH4_ctrl_std","K_ctrl_std","Mg_ctrl_std")

#creating the in columns, considering 2 reps of C, 3 of B, 3 of A (in this order), and how each is in triplicate

Cations_Ctrl_All<-data.frame(lapply(Cations_ctrl_mol_Avg[1,],rep,times=51))

#Anions
Anions_Ctrl_Avg<-data.frame(Anions_ctrl_mol %>%
    group_by(group = gl(n()/3, 3)) %>% #takes average of every 3 rows
        summarise_at(vars(Acetate,Chloride,Phosphate, Sulfate,Carbonate), list(mean = ~mean(., na.rm = TRUE), sd = ~sd(., na.rm = TRUE))))%>% 
  select(-1)
colnames(Anions_Ctrl_Avg)<-c("Ace_ctrl","Cl_ctrl","P_ctrl","S_ctrl","Carb_ctrl","Ace_ctrl_std","Cl_ctrl_std","P_ctrl_std","S_ctrl_std","Carb_ctrl_std")

Anions_Ctrl_All<-data.frame(lapply(Anions_Ctrl_Avg[1,],rep,times=51))
```

## Adding biochar mass, urine volume, and initial urine

edited Nov 2023 to include new columns

```{r}
#Cations

df_All<-data.frame(cbind(df_All,Cat_In,An_In,volume, mass_biochar, Cations_Ctrl_All, Anions_Ctrl_All))
```

## Calculating the Normalized Ion Concentrations and Dose

edited Nov 2023 to update reference value for columns being divided

```{r}
df_All$Na_Norm<- df_All$Sodium/df_All$Na_In
df_All$NH4_Norm<- df_All$Ammonium/df_All$NH4_In
df_All$K_Norm<- df_All$Potassium/df_All$K_In
df_All$Mg_Norm<- df_All$Magnesium/df_All$Mg_In

df_All$Ace_Norm<- df_All$Acetate/df_All$Ace_In
df_All$Cl_Norm<- df_All$Chloride/df_All$Cl_In
df_All$P_Norm<- df_All$Phosphate/df_All$P_In
df_All$S_Norm<- df_All$Sulfate/df_All$S_In
df_All$Carb_Norm<- df_All$Carbonate/df_All$Carb_In
```

## Determining Dose

```{r}
df_All$Dose<-(mapply('/',df_All$mass_biochar,df_All$volume))
```

## Calculating Q of each Triplicate

Note: the Q is based on the C_in which is the average of the initial value and the control

```{r}


Q_function<-function(df,Q,C_In,C_eq,volume,m_s) {
  df[[Q]]<-((df[[C_In]]-df[[C_eq]])*df[[volume]]/df[[m_s]])
  }

df_All$Q_NH4<-Q_function(df_All,"Q_NH4","NH4_In","Ammonium","volume","mass_biochar")
#----------------------------------------------------------------------

df_All$Q_Na<-Q_function(df_All,"Q_Na","Na_In","Sodium","volume","mass_biochar")
#----------------------------------------------------------------------

df_All$Q_K<-Q_function(df_All,"Q_K","K_In","Potassium","volume","mass_biochar")
#----------------------------------------------------------------------

df_All$Q_Mg<-Q_function(df_All,"Q_Mg","Mg_In","Magnesium","volume","mass_biochar")

#October 2023; adding Q for Anions

df_All$Q_Cl<-Q_function(df_All,"Q_Cl","Cl_In","Chloride","volume","mass_biochar")
#----------------------------------------------------------------------

df_All$Q_PO4<-Q_function(df_All,"Q_PO4","P_In","Phosphate","volume","mass_biochar")

#----------------------------------------------------------------------

df_All$Q_S<-Q_function(df_All,"Q_S","S_In","Sulfate","volume","mass_biochar")
#----------------------------------------------------------------------

df_All$Q_Ace<-Q_function(df_All,"Q_Ace","Ace_In","Acetate","volume","mass_biochar")
```

## Average and stdev of Replicates

-   Calculating the average and stdev of the replicates an combining them into one dataframe

-   calculating Q_sd as a percent of Q to determine where to cuz off the data

```{r}

#taking the average 

df_All_Avg<-data.frame(
 df_All %>%
   select(-PHREEQC_number, -Rep) %>%
    group_by(group = gl(n()/3, 3)) %>% #takes average of every 3 rows
     summarise(across(everything(), mean, na.rm = TRUE)))

#taking stdev
df_All_sd<-data.frame(
 df_All%>%
    group_by(group = gl(n()/3, 3)) %>% #applies function to every 3 rows
    summarise_at(c("Sodium","Ammonium","Potassium","Magnesium","Acetate","Chloride","Phosphate", "Sulfate", "Carbonate","pH","Ionic_str", "Act_NH4","Act_Na","Act_K","Na_Norm","NH4_Norm","K_Norm","Mg_Norm","Ace_Norm","Cl_Norm","P_Norm","S_Norm","Carb_Norm","Q_NH4","Q_Na","Q_K","Q_Mg","Q_Cl","Q_PO4","Q_S","Q_Ace"),sd))

colnames(df_All_sd)<-as.character(c("group","Sodium_sd","Ammonium_sd","Potassium_sd","Magnesium_sd","Acetate_sd","Chloride_sd","Phosphate_sd", "Sulfate_sd", "Carbonate_sd","pH_sd", "Ionic_str_sd","Act_NH4_sd","Act_Na_sd","Act_K_sd","Na_Norm_sd","NH4_Norm_sd","K_Norm_sd","Mg_Norm_sd","K_Ace_Norm_sd","Cl_Norm_sd","P_Norm_sd","S_Norm_sd","Carb_Norm_sd","Q_NH4_sd","Q_Na_sd","Q_K_sd","Q_Mg_sd","Q_Cl_sd","Q_PO4_sd","Q_S_sd","Q_Ace_sd"))

#combining average and std dataframes


df_All_Avg_sd<-data.frame(cbind(df_All_Avg,df_All_sd[,-1]))

#Calculating the %percent SD of Q

df_All_Avg_sd$Q_NH4_sd_perc<-(mapply('/', df_All_Avg_sd$Q_NH4_sd,df_All_Avg_sd$Q_NH4))
df_All_Avg_sd$Q_NH4_sd_perc<-(abs(mapply('*',df_All_Avg_sd$Q_NH4_sd_perc,100)))  

df_All_Avg_sd$Q_Na_sd_perc<-(mapply('/', df_All_Avg_sd$Q_Na_sd,df_All_Avg_sd$Q_Na))
df_All_Avg_sd$Q_Na_sd_perc<-(abs(mapply('*',df_All_Avg_sd$Q_Na_sd_perc,100))) 

df_All_Avg_sd$Q_K_sd_perc<-(mapply('/', df_All_Avg_sd$Q_K_sd,df_All_Avg_sd$Q_K))
df_All_Avg_sd$Q_K_sd_perc<-(abs(mapply('*',df_All_Avg_sd$Q_K_sd_perc,100))) 

df_All_Avg_sd$Q_Mg_sd_perc<-(mapply('/', df_All_Avg_sd$Q_Mg_sd,df_All_Avg_sd$Q_Mg))
df_All_Avg_sd$Q_Mg_sd_perc<-(abs(mapply('*',df_All_Avg_sd$Q_Mg_sd_perc,100))) 

#October 2023; adding Q for Anions
df_All_Avg_sd$Q_Cl_sd_perc<-(mapply('/', df_All_Avg_sd$Q_Cl_sd,df_All_Avg_sd$Q_Cl))
df_All_Avg_sd$Q_Cl_sd_perc<-(abs(mapply('*',df_All_Avg_sd$Q_Cl_sd_perc,100)))  

df_All_Avg_sd$Q_PO4_sd_perc<-(mapply('/', df_All_Avg_sd$Q_PO4_sd,df_All_Avg_sd$Q_PO4))
df_All_Avg_sd$Q_PO4_sd_perc<-(abs(mapply('*',df_All_Avg_sd$Q_PO4_sd_perc,100))) 

df_All_Avg_sd$Q_S_sd_perc<-(mapply('/', df_All_Avg_sd$Q_S_sd,df_All_Avg_sd$Q_S))
df_All_Avg_sd$Q_S_sd_perc<-(abs(mapply('*',df_All_Avg_sd$Q_S_sd_perc,100))) 

df_All_Avg_sd$Q_Ace_sd_perc<-(mapply('/', df_All_Avg_sd$Q_Ace_sd,df_All_Avg_sd$Q_Ace))
df_All_Avg_sd$Q_Ace_sd_perc<-(abs(mapply('*',df_All_Avg_sd$Q_Ace_sd_perc,100))) 

#------------------------------------------------------------------------------------------------------------
```

### Converting Ox condition to factors to be able to group for plotting

```{r}
df_All_Avg_sd$Ox<-as.factor(df_All_Avg$Ox) 
```

## Oct 2023 Edit

Resaving file as RDS to work on in separate .rmd file

Note - In is just in, not avg of in and ctrl - verifying

```{r}
saveRDS(df_All_Avg_sd, file = "int_ALL.RDS")

```
